Growth Resilience

### 2017-06-20 analysis/analysis_resilience_bai.Rmd
updating reslience BAI analysis

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
# library("detrendeR")
library("pander")
library('boot')
library('gtable')
library('grid')
```

@@

```{r, echo=FALSE}
#machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

```{r}
source(paste0(di, 'script/R/rw_byTree.R'))
source(paste0(di, 'script/R/bai_piovesan.R'))
```

@@

# Cómputo del BAI por site

@@

## Resilience function

```{r}

event_year <- c(1995, 2005, 2012)

window <- c(2,3) 
  i <- 1995
  window <- 3
  bai_object <- bai_sj

baiResilience <- function(bai_object, event_years, window){

  out_growth <- c() 
  out_res <- c() 
  out <- list()

  for (i in event_years){
    # Create df previous, during and post event
    df <- bai_object %>% 
      mutate(year = as.numeric(row.names(.))) %>% as.data.frame()

    df_pre <- df %>% filter(year < i & year >= (i - window)) %>% mutate(disturb = 'pre')
    df_event <- df %>% filter(year == i) %>% mutate(disturb = 'dr')
    df_post <- df %>% filter(year > i & year <= (i + window)) %>% mutate(disturb = 'post')

    # Melt data 
    dfmelt <- bind_rows(df_pre, df_event, df_post) %>% 
      gather(tree, value, -disturb, -year)

    # Compute mean of Growth (previous, during and posterior)
    growth_df <- dfmelt %>% group_by(disturb, tree) %>% 
      summarise(mean_period = mean(value),
                sd_period = sd(value),
                se_period = sd_period/sqrt(length(value))) %>% 
      mutate(disturb_year = i)

    out_growth <- rbind(out_growth, growth_df)

    # Compute resilience by trees 
    aux_resilience <- c() 
    trees <- unique(growth_df$tree)

    for (t in trees){
      # Filter by tree
      df_tree <- growth_df %>% filter(tree == t)

      # Compute resilience metrics by tree
      aux_df <- df_tree %>% select(-c(tree, sd_period, se_period)) %>% 
        spread(key=disturb, value=mean_period) %>% 
        mutate(rt = dr / pre,
               rc = post / dr,
               rs = post / pre,
               rrs = (post - dr) / pre,tree = t) %>% 
        select(rt, rc, rs, rrs, disturb_year, tree)

      aux_resilience <- rbind(aux_resilience, aux_df)
    }

    out_res <- rbind(out_res, aux_resilience)
  }

  out$growth <- out_growth
  out$resilience <- out_res

  return(out)
}

dyears <- c(1995, 2005, 2012)
res_sj3 <- baiResilience(bai_sj, event_years = dyears, window = 3)
res_sj2 <- baiResilience(bai_sj, event_years = dyears, window = 2)

resile2 <- res_sj2$resilience
resile3 <- res_sj3$resilience

summary(lm(resile2$rs~resile3$rs))

>>>>

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("dplR")
library("stringr")
library("knitr")
library('gtable')
library('grid')
library('gridExtra')
```

@@

```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

```{r}
source(paste0(di, 'script/R/rw_byTree.R'))
source(paste0(di, 'script/R/bai_piovesan.R'))
source(paste0(di, 'script/R/baiResilience.R'))
```

@@

## Cómputo del BAI por site

@@

## Resilience

* Computar métricas de resiliencia BAI para los tres sitios. 
* Computar tres eventos climáticos: 1995, 2005, 2012
* Computar dos ventanas temporales: 2 y 3

```{r}
# Drought years 
dyears <- c(1995, 2005, 2012)

# SJ 
res_3_sj <- baiResilience(bai_sj, event_years = dyears, window = 3)
res_2_sj <- baiResilience(bai_sj, event_years = dyears, window = 2)

# caL 
res_3_caL <- baiResilience(bai_caL, event_years = dyears, window = 3)
res_2_caL <- baiResilience(bai_caL, event_years = dyears, window = 2)

# caH 
res_3_caH <- baiResilience(bai_caH, event_years = dyears, window = 3)
res_2_caH <- baiResilience(bai_caH, event_years = dyears, window = 2)
```

* Computar correlaciones ventanas temporales

```{r}
# Vector with objects name
obj <- c('res_2_sj', 'res_3_sj',
         'res_2_caL', 'res_3_caL',
         'res_2_caH', 'res_3_caH')

variables <- c('rt', 'rs', 'rc', 'rrs')

correla_ws <- c()

for (i in obj){ 
  x <- get(i)
  xres <- x$resilience
  out <- xres %>% 
    mutate(ws = paste0('ws_', as.character(str_extract(i, "([0-9])"))),
           site = str_replace(i, "res_[0-9]_", '')) %>%
    select(-disturb_year, -tree)

  correla_ws <- bind_rows(correla_ws, out)

}

# Split by window size 
correla <- correla_ws %>% split(.$ws)

# Change names 
names(correla[["ws_2"]])[1:4] <- paste0(names(correla[["ws_2"]])[1:4], '2')
names(correla[["ws_3"]])[1:4] <- paste0(names(correla[["ws_3"]])[1:4], '3')

cor2 <- correla[["ws_2"]] %>% select(-ws) %>% mutate(ind = row_number())
cor3 <- correla[["ws_3"]] %>% select(-ws) %>% mutate(ind = row_number())

correlations <- inner_join(cor2, cor3, by='ind')

# Resistance
model <- lm(rt2~rt3, data=correlations)
p_rt <- correlations %>% ggplot(aes(rt2, rt3)) + 
  geom_point(aes(colour=site.x)) + theme_bw() + geom_smooth(method = 'lm', se=FALSE) + 
  ggtitle(paste('rt (R2) = ', round(summary(model)$r.squared, 3)))

# Recovery
model <- lm(rc2~rc3, data=correlations)
p_rc <- correlations %>% ggplot(aes(rc2, rc3)) + 
  geom_point(aes(colour=site.x)) + theme_bw() + geom_smooth(method = 'lm', se=FALSE) + 
  ggtitle(paste('rc (R2) = ', round(summary(model)$r.squared, 3)))

# Resilience
model <- lm(rs2~rs3, data=correlations)
p_rs <- correlations %>% ggplot(aes(rs2, rs3)) + 
  geom_point(aes(colour=site.x)) + theme_bw() + geom_smooth(method = 'lm', se=FALSE) + 
  ggtitle(paste('rs (R2) = ', round(summary(model)$r.squared, 3)))

# Relative Resilience
model <- lm(rrs2~rrs3, data=correlations)
p_rrs <- correlations %>% ggplot(aes(rrs2, rrs3)) + 
  geom_point(aes(colour=site.x)) + theme_bw() + geom_smooth(method = 'lm', se=FALSE) + 
  ggtitle(paste('rrs (R2) = ', round(summary(model)$r.squared, 3)))

grid.arrange(p_rc, p_rt, p_rs, p_rrs, ncol=2) 
```
